Rclean: A Tool for Writing Cleaner, More Transparent Code

### 2020-02-05 joss/paper.Rmd
Fix new line in caption for prov figure
Fix new line issue with comment for code_graph example
Fixes citation issues from ref in text

At the core of the growth of scientific computation, the ``R``
statistical programming language has grown exponentially to become one
of the top ten programming languages in use today. At it's root R is a
*statistical* programming language. That is, it was designed for use
in analytical workflows; and the majority of the R community is
focused on producing code for idiosyncratic projects that are
*results* oriented. Also, R's design is intentionally at a level that
abstracts many aspects of programming that would otherwise act as a
barrier to entry for many users. This is good in that there are many
people who use R to their benefit with little to no formal training in
computer science or software engineering, but these same users can
also be frequently frustrated by code that is fragile, buggy and
complicated enough to quickly become obtuse even to the authors. The
stability, reproducibility and re-use of scientific analyses in R
would be improved by refactoring, which is a common practice in
software engineering [Martin2009CleanCraftsmanship]. From this
perspective, tools that can lower the time and energy required to
refactor analytical scripts and otherwise help to "clean" code, but
abstracted enough to be easily accessible, could have a significant
impact on scientific reproducibility across all disciplines
[@Visser2015].

@@

```{R long-script, echo = FALSE, eval = TRUE}

readLines(script)

>>>>

At the core of the growth of scientific computation, the ``R``
statistical programming language has grown exponentially to become one
of the top ten programming languages in use today. At it's root R is a
*statistical* programming language. That is, it was designed for use
in analytical workflows; and the majority of the R community is
focused on producing code for idiosyncratic projects that are
*results* oriented. Also, R's design is intentionally at a level that
abstracts many aspects of programming that would otherwise act as a
barrier to entry for many users. This is good in that there are many
people who use R to their benefit with little to no formal training in
computer science or software engineering, but these same users can
also be frequently frustrated by code that is fragile, buggy and
complicated enough to quickly become obtuse even to the authors. The
stability, reproducibility and re-use of scientific analyses in R
would be improved by refactoring, which is a common practice in
software engineering [@Martin2009CleanCraftsmanship]. From this
perspective, tools that can lower the time and energy required to
refactor analytical scripts and otherwise help to "clean" code, but
abstracted enough to be easily accessible, could have a significant
impact on scientific reproducibility across all disciplines
[@Visser2015].

@@

```{R long-script, echo = FALSE, eval = FALSE}

library(stats)
x <- 1:100
x <- log(x)
x <- x * 2
x <- lapply(x, rep, times = 4)
### This is a note that I made for myself.
### Next time, make sure to use a different analysis.
### Also, check with someone about how to run some other analysis.
x <- do.call(cbind, x)

### Now I'm going to create a different variable.
### This is the best variable the world has ever seen.

x2 <- sample(10:1000, 100)
x2 <- lapply(x2, rnorm)

### Wait, now I had another thought about x that I want to work through.

x <- x * 2
colnames(x) <- paste0("X", seq_len(ncol(x)))
rownames(x) <- LETTERS[seq_len(nrow(x))]
x <- t(x)
x[, "A"] <- sqrt(x[, "A"])

for (i in seq_along(colnames(x))) {
    set.seed(17)
    x[, i] <- x[, i] + runif(length(x[, i]), -1, 1)
}

### Ok. Now I can get back to x2.
### Now I just need to check out a bunch of stuff with it.

lapply(x2, length)[1]
max(unlist(lapply(x2, length)))
range(unlist(lapply(x2, length)))
head(x2[[1]])
tail(x2[[1]])

## Now, based on that stuff, I need to subset x2.

x2 <- lapply(x2, function(x) x[1:10])

## And turn it into a matrix.
x2 <- do.call(rbind, x2)

## Now, based on x2, I need to create x3.
x3 <- x2[, 1:2]
x3 <- apply(x3, 2, round, digits = 3)

## Oh wait! Another thought about x.

x[, 1] <- x[, 1] * 2 + 10
x[, 2] <- x[, 1] + x[, 2]
x[, "A"] <- x[, "A"] * 2

## Now, I want to run an analysis on two variables in x2 and x3.

fit.23 <- lm(x2 ~ x3, data = data.frame(x2[, 1], x3[, 1]))
summary(fit.23)

## And while I'm at it, I should do an analysis on x.

x <- data.frame(x)
fit.xx <- lm(A~B, data = x)
summary(fit.xx)
shapiro.test(residuals(fit.xx))

## Ah, it looks like I should probably transform A.
## Let's try that.
fit_sqrt_A <- lm(I(sqrt(A))~B, data = x)
summary(fit_sqrt_A)
shapiro.test(residuals(fit_sqrt_A))

## Looks good!

## After that. I came back and ran another analysis with 
## x2 and a new variable.

z <- c(rep("A", nrow(x2) / 2), rep("B", nrow(x2) / 2))
fit_anova <- aov(x2 ~ z, data = data.frame(x2 = x2[, 1], z))
summary(fit_anova)
